---
title: "Data Products Final Project"
author: "Pablo Ordonez"
date: "8/9/2019"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Shiny App: Global Equity Market Valuations

This is my presentation pitch for the Coursera Data Products Final Course Project. The shiny app develpod explores data on global equity market valuations.

- The first tab in the app shows a leaflet map showing a color map for global equity market valuations.
- The second tab in the app shows the time series detial for each country, using Shiny's reactivness functions to loop through different countries.
- The final tab shows the reference to understand the purpose of the app and some links to external documentation and to the Github repository for the code.


Github code:https://github.com/OrdonezPablo/coursera-data-products-project

Shiny app: https://ordonezpablo.shinyapps.io/project_final/



### First tab: Global Equity Market Valuations

- In this first tab we used the leaflet library, also part of the Data proudcts course material.
- We used a global map using a shapfile found here thematicmapping.org
- We then crossed the data with the shapefile data.
- The code below illustrates an example of the map 

```{r leaflet map, echo = TRUE, eval=FALSE}

#load shape file, csv and merge data
sfdf <- readOGR(dsn = getwd(), layer = "TM_WORLD_BORDERS-0.3")
country_pe <- read_excel("./country pe.xlsx", 
                         sheet = "spot pe (value)", skip = 4)
mymerge <- merge(sfdf, country_pe, by = "NAME")

#example of code for leaflet map
leaflet(data = mymerge) %>% 
  addTiles() %>% 
  setView( lat = 10, lng = 0, zoom = 1) %>% 
  addPolygons

```

### Second tab: Global Equity Market Valuations

- In this second tab we had two objectives
- using the reactive benefits from shiny to scroll through different countries
- and illustration each market's P/E multipe with the plotly chart application to ggplots

```{r plotly_charts, echo = TRUE, eval=FALSE}

selectedData <- reactive({
        
        pe_ts_long %>% 
            filter(index == input$index) %>% 
            mutate(mean = mean(pe))
        
    })
    
    output$plot1 <- renderPlotly({
        ggplot(selectedData(), aes(Date, pe)) +
            geom_line() +
            geom_hline(aes(yintercept=mean)) +
            labs(
                y = "Price to Earnings Ratio",
                x = "Date"
            )
    })

```

### Coursera Data Products Project

Thanks!